Adaptive Test

### 2023-10-16 scripts/validation_ML_estimator.Rmd

ggplot(df, aes(x = error))+
  geom_density(fill = "grey", col = NA)+
  geom_jitter(aes(y = 0), pch = 1, width = 0.0001, alpha = 0.1, size =5)+
  xlim(-0.0015,0.0015)+
  labs(x = "Difference between Javascript and catR estimates", y = "Count")+
  theme_few()

>>>>

ggplot(df, aes(x = error))+
  geom_density(fill = "grey", col = NA)+
  geom_jitter(aes(y = 0), pch = 1, width = 0.0001, alpha = 0.1, size =5)+
  xlim(-0.0015,0.0015)+
  labs(x = "Difference between JavaScript and catR estimates", y = "Count")+
  theme_few()
